---
title: "European Bank Capitalization Levels"
author: "Nicholas Chung and Christopher Gandrud"
date: "29 July 2014"
output: 
    html_document:
        theme: null
        css: /git_repositories/Tier1StyleGuide/css/Tier1Main.css
---

```{r include=FALSE}
# Load packages
library(dplyr)
library(rCharts)
library(DataCombine)
library(xtable)

# Load capitalisation data
MainData <- read.csv('data/CapitalData.csv', stringsAsFactors=FALSE)
```

> In this report we present an overview of European bank's capitalization levels.

## Comparison to Other Regions

Over the past three years European banks have been increasing their capital levels relative to East Asian and North American Banks.

#### Median Bank Capital to Total Assets (%)

```{r message=FALSE, echo=FALSE, results='asis'}
# Find yearly medians
MainAll <- group_by(MainData, region, year)
MedianData <- summarise(MainAll, MedianCap = median(FB.BNK.CAPA.ZS, na.rm = TRUE))                                             

# Plot
Plot1 <- nPlot(MedianCap~year, group = 'region', type = "lineChart", 
               data =  MedianData)

Plot1$chart(forceY = c(0, 12))
Plot1$set(width = 700, height = 300)
Plot1$show('inline', include_assets = TRUE, cdn = TRUE)
````

Source: World Bank. *Click individual countries to highlight/hide.*

## Comparison of Bank Capitalization Levels Across European Regions

Within Europe the banks in the Caucasus have the highest median capitalization levels, though the level has been declining. While Southwestern, Nordic and Western European banks tend to have the lowest capitalization levels. 

#### Median Bank Capital to Total Assets (%), by European Region

```{r message=FALSE, echo=FALSE, results='asis'}
# Keep only European countries
Europe <- DropNA(MainData, 'EuropeanRegions')

# Find yearly medians
EuropeGrouped <-group_by(Europe, EuropeanRegions, year)
MedianEurope <- summarise(EuropeGrouped, MedianCap = median(FB.BNK.CAPA.ZS, 
                                                            na.rm = TRUE))                                             

# Plot
Plot1 <- nPlot(MedianCap~year, group = 'EuropeanRegions', type = "lineChart", 
               data =  MedianEurope)

Plot1$chart(forceY = c(0, 25))
Plot1$set(width = 700, height = 300)
Plot1$show('inline', include_assets = TRUE, cdn = TRUE)
```

Source: World Bank. *Click individual countries to highlight/hide.*

## Western Europe

Western Europe is by far the most critically under-capitalized region within Europe with an average, regional capital ratio of 6.33%. The Netherlands in particular had the lowest capitalization levels at 4.8% in 2013.

#### Median Bank Capital to Total Assets (%), Western European Countries

```{r message=FALSE, echo=FALSE, results='asis'}
# Keep only Western Eurpean Countries
WEurope <- subset(MainData, EuropeanRegions == 'Western Europe')

WEuropeGrouped <- group_by(WEurope, country, year)
MedianWE <- summarise(WEuropeGrouped, MedianCap = median(FB.BNK.CAPA.ZS, 
                                                            na.rm = TRUE))  

# Plot
Plot1 <- nPlot(MedianCap~year, group = 'country', type = "lineChart", 
               data =  MedianWE)

Plot1$chart(forceY = c(0, 10))
Plot1$set(width = 700, height = 300)
Plot1$show('inline', include_assets = TRUE, cdn = TRUE)
```

Source: World Bank. *Click individual countries to highlight/hide.*

## 2013 Country Summaries

#### 2013 Median Bank Capital to Total Assets (%), by country

```{r message=FALSE, echo=FALSE, results='asis'}
Europe2013 <- subset(Europe, year == 2013)

# Order from lowest to highest
Europe2013 <- arrange(Europe2013, FB.BNK.CAPA.ZS)
Europe2013$FB.BNK.CAPA.ZS <- round(Europe2013$FB.BNK.CAPA.ZS, digits = 2)
Europe2013$FB.BNK.CAPA.ZS[is.na(Europe2013$FB.BNK.CAPA.ZS)] <- 'No Data'

# Clean
Europe2013 <- Europe2013[, c('country', 'FB.BNK.CAPA.ZS')]
names(Europe2013) <- c('Country', 'Bank capital/assets (%)')

# Replace NA with No Data


Table2013 <- xtable(Europe2013, )
print(Table2013, type = 'html', include.rownames = FALSE, hline.after = NULL)
```

<p class="footer">Copyright &copy; 2014 Tier 1 Exchange LLC. All Rights Reserved.</p>
